---
title: "introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(binomial)
```

#Bin Choose
calculates the number of combinations in which k successes can occur in n trials
```{r}
bin_choose(5,3)
```

#Bin Variable
return the binomial variables
```{r}
bin_variable(5, 0.5)
```

#Bin Probability
calculates the probability in which k successes can occur in n trials
```{r}
bin_probability(3, 5, 0.5)
```

#Bin Mean
return the mean of the binomial distribution
```{r}
bin_mean(5, 0.5)
```

#Bin Variance
return the variance of the binomial distribution
```{r}
bin_variance(5, 0.5)
```

#Bin Mode
return the mode of the binomial distribution
```{r}
bin_mode(5, 0.5)
```

#Bin Skewness
return the skewness of the binomial distribution
```{r}
bin_skewness(5, 0.5)
```

#Bin Kurtosis
return the kurtosis of the binomial distribution
```{r}
bin_kurtosis(5, 0.5)
```

#Bin Distribution
return the distribution of success
```{r}
bin_distribution(5, 0.5)
```

#Bin Cumulative
return the distribution of success with cumulative probability
```{r}
bin_cumulative(5, 0.5)
```
